EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-17 paper/paper.tex
update

@@

\subsection{User Interface}
EasyMerge has a simple and straightforward user interface, as shown in figure.

>>>>

\begin{figure*}
\centering
\epsfig{file=screen.pdf}
\caption{EasyMerge User Interface}
\end{figure*}

@@

\subsection{User Interface}
EasyMerge has a simple and straightforward user interface, as shown in {\bf Figure 1}.
Once the program is launched, user can click ``Open Source" at top left and then choose the folder 
where the software project's source tree resides in the popup open directory dialog.
Then by clicking ``Analyze" button on the right side, EasyMerge starts analyzing the selected source tree.

There are five text boxes displayed on the main interface.
Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record.

User can click each item in the ``Possible Merges" list. When one item is selected, a corresponding clone set will be loaded. All files
associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI.
Inside the source code browser, code fragment that
